Standardized crypto-loans on Cardano blockchain\textquotedblright \thanks{Supported by organization x.}

### 2021-02-02 papers/actus2021/article.tex
more

\begin{document}
\title{Contribution Title\thanks{Supported by organization x.}}

@@

@@

This is due to the risk factor's state not being known at instantiation
time. In the case of Cardano blockchain, these values are usually
provided through an ``Oracle'' mechanism. Oracle could be a trusted
party providing necessary data or network of parties under consensus
{[}find a quote{]}. From Marlowe DSL perspective, the exact mechanism
that provides external data is less important, as Marlowe abstracts
over IO by requiring particular type of input (``Choice'') protected
with a cryptographic signature (Choice owner), although Plutus implementation
of Marlowe only supports {[}Cardano Elliptic Curves - which ones?{]}
so adding new types of signatures would require some extra work. As
a result, the event of receiving data from Oracle is treated the same
as receiving integer numbers from user input in other languages

\section{Building executable specification of ACTUS for crypto-loans}

@@

\begin{equation}
formula(st)=\begin{cases}
formula' & var1(st)<var2(st)\\
0 & otherwise
\end{cases}
\end{equation}

@@

Generated contract is essentially a continuation chain of repetition
Marlowe Contracts:

@@

\begin{figure}
\includegraphics[width=1\textwidth]{flowchart} \caption{Modules responsible for contract generation.}
\label{fig1-1-1} 
\end{figure}

>>>>

\begin{document}
\title{Standardized crypto-loans on Cardano blockchain\textquotedblright \thanks{Supported by organization x.}}

@@

List of contributions:
\begin{itemize}
\item \textquotedblleft Marlowe Labs\textquotedblright{} editor on Playground
(Dmytro) 
\item R Shiny cashflow visualiser for ACTUS (Dmytro) 
\item ACTUS Utility functions (Dmytro, Quanterall) 
\item executable ACTUS spec for PAM (Dmytro, Alex) 
\item executable ACTUS spec for LAM (Wyo Hackathon) 
\item Library for generating ACTUS contracts (Dmytro) 
\item ACTUS-like examples on Playground (Dmytro, Alex, Pablo) 
\item Marlowe DSL enhancements for Actus: Cond, Mul (Dmytro) (draft) 
\item ACTUS spec generator for Agda (Dmytro) 
\item Auto-refund static analysis (Pablo) (partial: only QC) 
\item Verification with QC + SMT (Dmytro) 
\end{itemize}

@@

This is due to the risk factor's state not being known at instantiation
time. In the case of Cardano blockchain, these values are usually
provided through an ``Oracle'' mechanism. Oracle could be a trusted
party providing necessary data or network of parties under consensus
{[}find a quote{]}. From Marlowe DSL perspective, the exact mechanism
that provides external data is less important, as Marlowe abstracts
over IO by requiring particular type of input (``Choice'') protected
with a cryptographic signature (Choice owner). As a result, the event
of receiving data from Oracle is treated the same as receiving integer
numbers from user input in other languages

\section{Building executable specification of ACTUS}

@@

\begin{equation}
formula(st)=\begin{cases}
formula'(st) & var1(st)<var2(st)\\
0 & otherwise
\end{cases}
\end{equation}

@@

Generated contract is essentially a continuation chain of smaller
contracts:

@@

\begin{figure}
\includegraphics[width=1\textwidth]{flowchart} \caption{Chain of sub-contracts representing ACTUS logic}
\label{fig1-1-1} 
\end{figure}
